---
title: "McDonald's Review Sentiment"
author: "Van Quoc Mai, maiquocvan@gmail.com"
date: "April 7, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Dataset

Data [McDonalds-Yelp-Sentiment-DFE.csv](https://www.crowdflower.com/wp-content/uploads/2016/03/McDonalds-Yelp-Sentiment-DFE.csv) is get from https://www.crowdflower.com

## Description of Variables

The dataset contains 1525 abservations of 10 variables:

1. **unit_id**: id of record
2. **golden**: value *FALSE*
3. **unit_state**: value *finalized*
4. **trusted_judgments**: value *3*
5. **last_judgment_at**: time. Example *2/21/15 0:36*
6. **policies_violated**: the type of policies, violated. Example: *RudeService\nOrderProblem\nFilthy* 
7. **policies_violated.confidence**: the confidence of policies, violated. Example: *1.0\n0.6667\n0.6667*
8. **city**: City name
9. **policies_violated_gold**: value *NA*
10. **review**: review detail

## Problem Statement
A sentiment analysis of negative McDonald's reviews. Contributors were given reviews culled from low-rated McDonald's from random metro areas and asked to classify why the locations received low reviews. Options given were:

  - Rude Service
  - Slow Service
  - Problem with Order
  - Bad Food
  - Bad Neighborhood
  - Dirty Location
  - Cost
  - Missing Item

## Data Pre-Processing

The column names of data
```{r echo=FALSE}
data <- read.csv('../data/McDonalds-Yelp-Sentiment-DFE.csv')
names(data)
```

Summary the data, the content of 'review' column is too long. So we ignore it
```{r echo=FALSE}
summary(data[, -10])
```

The detail of data
```{r echo=FALSE}
head(data[, 1:9])
```

and the content of 'review' column
```{r echo=FALSE}
head(data[1:2, 10])
```
There are some fields that there is no meaning. Such as:

- unit_id
- last_judgment_at
- policies_violated_gold (all values = 'NA')
- golden
- unit_state
- trusted_judgments
So remove them
```{r echo=FALSE}
data <- data[, c(-1, -5)]
data$policies_violated_gold <- NULL
data$X_golden <- NULL
data$X_unit_state <- NULL
data$X_trusted_judgments <- NULL
```

Let's see the detail after cleaning
```{r echo=FALSE}
dim(data)
names(data)
```

## Data Exploration
Summary the data
```{r echo=FALSE}
summary(data[, 1:3])
```

## Data Visualization
How many records that each city has?
```{r echo=FALSE}
library(ggplot2)
ggplot(data, aes(city)) + geom_bar()
```

## Creating New Features

There are relationship between 'policies_violated' vs. 'policies_violated.confidence'. We should create new fields base on  'policies_violated' with value from 'policies_violated.confidence'

Firstly, we should remove the missed value. 
policies_violated = 'na' or policies_violated = '' is no meaning. So remove those records
```{r echo=FALSE}
dim(data[data$policies_violated == 'na', ])
data <- data[data$policies_violated != 'na', ]
dim(data[data$policies_violated == '', ])
data <- data[data$policies_violated != '', ]
```

Let's see the result
```{r echo=FALSE}
parse_policies_violated <- function(dat = data){
  # First: type of 'policies_violated' is factor. So convert it to characters
  dat$policies_violated <- as.character(dat$policies_violated)
  # Second: there are duplicates, just review uinque
  uni_policies_violated <- unique(data$policies_violated)
  for(options in uni_policies_violated){
    arr_option = strsplit(options, '\n')
    # type of arr_option is list, so we use [[1]] to get the value
    for(option in arr_option[[1]]){
      # Not do anything if 'option' exists
      if(any(option == names(dat))){
        
      } else {
        new_col <- 0
        dat <- cbind(dat, new_col)
        names(dat)[length(names(dat))] <- option
      }
      
    }
  }
  
  return(dat)
}

data <- parse_policies_violated(data)

# Let's see the new fields
names(data)
head(data[, 5:13])

parse_policies_violated.confidence <- function(dat = data){
  # First: type of 'policies_violated' is factor. So convert it to characters
  dat$policies_violated.confidence <- as.character(dat$policies_violated.confidence)
  dat$policies_violated <- as.character(dat$policies_violated)
  for(i in 1:nrow(dat)){
    confid.list = strsplit(dat$policies_violated.confidence[i], '\n')
    option.list = strsplit(dat$policies_violated[i], '\n')
    # strsplit() return a list, so we use [[1]] to get the value
    for(j in 1:length(option.list[[1]])){
      dat[i, option.list[[1]][j]] <- confid.list[[1]][j]
    }
  }
  
  return(dat)
}

data <- parse_policies_violated.confidence(data)

# 'na' field has no meaning. Remove it.
data$na <- NULL
names(data)
head(data[, 5:12])
```

Next:

- We will ignore 'review'
- Group by 'city', calculate the mean of values (ignore the record has 0 values)
```{r echo=FALSE}
# Convert all policies violated fields to number
for(i in 5:12){
  data[, i] <- as.numeric(data[, i])
}
# summary but ignore 'review'
#summary(data[, -4])


# Groupby 'city', calculate the mean
avg.city.policies.violated <- function(dat = data){
  cities <- unique(dat$city)
  # Remove empty city
  cities <- cities[cities != '']
  avg.df <- data.frame()
  
  for(city in cities){
    # apply() - option: 1-row, 2-column
    avg.col.by.city <- apply(dat[dat$city == city, 5:12], 2, function(x) {
      mean(x[x != 0])
    })
    avg.df <- rbind(avg.df, avg.col.by.city)
  }
  # Add city column at the end data frame
  avg.df <- cbind(avg.df, as.character(cities))
  names(avg.df) <- names(dat)[c(5:12, 3)]
  
  return(avg.df)
}

avg.cities <- avg.city.policies.violated(dat = data)
```

Let's see the result:
```{r echo=FALSE}
head(avg.cities)
```

## Modeling: 


In-progress!

